Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-06-27 Latex/journal_v1/V5/pr.tex
latex abstract

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\setlength{\columnsep}{11mm}
\begin{document}

\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{abstract}

\end{abstract}

@@

\begin{figure}
  \centering 
    %\includegraphics[scale = 0.4]{Drawing13.pdf}
    \includegraphics[scale = 0.4]{Drawing13.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
Next we introduce two methods which are both greedy algorithm.
The first method is a greedy algorithm that assign one O-RU to each UE and the second method is
a greedy algorithm that assign one or more than one O-RU to each UE and use coordinated multipoint (CoMP) transmissions \cite{yang2021multicast}.
\begin{enumerate}
\item\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}

@@

& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{p12}\\

@@

The problem \eqref{problem2} is an integer linear programming.
By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
the problem \eqref{problem2} becomes to an NP-complete 0-1 multiple knapsack problem.  

@@

The complexity of this algorithm is about $O(Slog(s)) + O(R\times \mathfrak{N})$.

@@

@@

\item\textit{Greedy Algorithm for Comp O-RU Assignment:}
Here we want to solve problem \eqref{problem2}, by assuming that one or more than one O-RU can assign to each UE.
We solve this problem using GACA algorithm which used GAAOU algorithm.
In this algorithm, Firstly we sort slices based on their priority (So the UEs of slices are sorted too).
Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
\State Set $\mathtt{R}^{t} = 0$
\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\For {$s \gets 1$ to $S$}
\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\State $g^{r^*}_{u(s,i)} = 1$ 
\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
\State Set $g^{r^*}_{u(s,i)} = 0$
\State update $\mathtt{R}^{t}$
\end{enumerate}

@@

\For {$i \gets 1$ to $Iter_{max}$}\label{33}

@@

>>>>

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\setlength{\columnsep}{11mm}
\begin{document}

\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{abstract}
Nowadays, RAN virtualization attracts a lot of attention from operators since it 
has significant benefits which leads to increase the flexibility and 
reduce operator costs
such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
Also, Openness and Flexibility are two other principle points that encourage Open Radio Access Network (O-RAN)
Alliance to establish O-RAN as a next generation of RAN systems. 
O-RAN is a combination of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
Central Unit (O-CU).
O-DU and O-CU are

Network Slicing, is an end-to-end logical network
which offers services with special needs. Multiple network Slices in the same infrastructure run and manage
and work independently.

In this paper, resource allocation in an O-RAN system is considered using the concept of network slicing.
The problem of O-RU assignment, power allocation and 
\end{abstract}

@@

\begin{figure}
  \centering 
    \includegraphics[scale = 0.35]{Drawing15.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[height=\textheight/2,width=\textwidth/2]{Drawing14.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\

@@

Assume $\boldsymbol{P}$ and $\boldsymbol{E}$ are fixed, we want to find $\boldsymbol{G}$.
Next we introduce a greedy algorithm that assign one O-RU to each UE.

\textit{Greedy Algorithm for Non-Comp O-RU Assignment:}

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{p12}\\

@@

%The problem \eqref{problem2} is an integer linear programming.
%By changing inequality \eqref{p12} to equality ($\sum_{r}g^r_{u(s,i)} = 1$),
The problem \eqref{problem2} is an NP-complete 0-1 multiple knapsack problem.  

@@

The complexity of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.

@@

\State Set ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$

@@

@@

\For {$i \gets 1$ to $Iter_{max}$}\label{23}

@@

\State \textbf{end for} \label{24}
